---
title: "viz_part_1"
author: "Jiayi Yang"
date: "2022-10-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## import data

```{r}
library(tidyverse)
library(ggridges)
```

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

let's make a scatterplot

```{r}
ggplot(weather_df, aes (x = tmin, y = tmax)) +
  geom_point()
```

Let's make the same scatterplot but different

```{r}

weather_df %>% 
  drop_na() %>% 
  filter (name == "CentralPark_NY") %>% 
  ggplot(aes (x = tmin, y = tmax)) +
  geom_point()
```

Let's make the same scatterplot but different
```{r}
weather_scatterplot = 
  weather_df %>% 
  drop_na() %>% 
  ggplot(aes(x = tmin, y = tmax))

weather_scatterplot +
  geom_point()
```
## Let's fancy this up a bit

```{r}
weather_df %>% 
  ggplot(aes (x = tmin, y = tmax, color = name)) +
  geom_point(alpha = .3) +
  geom_smooth(se = FALSE)
```

Maybe make seperate panels

```{r}
weather_df %>% 
  ggplot(aes (x = tmin, y = tmax, color = name)) +
  geom_point(alpha = .3) +
  geom_smooth(se = FALSE) +
  facet_grid(. ~ name)

```

`tmax` and `tmin` is boring, let's spice it up some.
```{r}

weather_df %>% 
  ggplot(aes(x = date, y = tmax, size = prcp, color = name)) +
  geom_point (alpha = .3) +
  geom_smooth (se = FALSE) +
  facet_grid (. ~ name)
```

## some quick stuff
```{r}

weather_df %>% 
  ggplot (aes(x = tmin, y = tmax)) +
  geom_hex()
  
```
## Univariate plots
Histograms, boxplots, violins...

```{r}

weather_df %>% 
  ggplot(aes(x = tmax, color = name)) +
  geom_histogram() +
  facet_grid(. ~ name)
```

Let's see more options

```{r}
weather_df %>% 
  ggplot(aes(x = tmax, fill = name)) +
  geom_density(alpha = .3)
```
Boxplots

```{r}
weather_df %>% 
  ggplot(aes(x = name, y = tmax, fill = name))+
  geom_violin()
```

OR

```{r}
weather_df %>% 
  ggplot(aes(x = tmax, y = name)) +
  geom_density_ridges()
```


## saving and embedding plots
First, lets save a plot.
```{r}
weather_scatterplot = 
  weather_df %>% 
  ggplot(aes(x = date, y = tmax, color = name, size = prcp)) +
  geom_point(aes(size = prcp), alpha = .3) +
  geom_smooth (se = FALSE) +
  facet_grid(. ~ name)
weather_scatterplot

ggsave(file = "weather_scatterplot.pdf", 
       plot = weather_scatterplot, 
       width = 8, height = 5)
```
```{r}
weather_scatterplot
```


